Guide for manual trajectory inference

### 2018-07-05 scripts/evaluate_toy/1-methods-toys.Rmd
dataset -> task

data("toy_tasks")
tasks <- toy_tasks
```

```{r}
tasks$counts <- map(tasks$counts, function(counts) {
  cbind2(counts, matrix(sample(1:100, nrow(counts)*100, replace=TRUE), nrow=nrow(counts))) %>% {magrittr::set_colnames(., paste0("G", 1:ncol(.)))}
})
task <- dynutils::extract_row_to_list(tasks, 3)
pheatmap::pheatmap(task$counts)

source("~/thesis/projects/dynverse/dynmodular/dimred_wrappers.R")
# space <- task$counts %>% dimred_dp(2, neigen=2) %>% as.data.frame
space <- task$counts %>% dimred_mds(2) %>% as.data.frame
# space <- task$counts %>% dimred_lle(2) %>% as.data.frame
space <- space %>% bind_cols(task$prior_information$grouping_assignment %>% slice(match(rownames(task$counts), cell_id)))
space %>%  ggplot() + geom_point(aes(Comp1, Comp2, color=group_id))
```

@@

  # factory(function() {
    dyneval:::evaluate_ti_method(tasks, method, params, metrics = metric_names, timeout = 100)
  # }
  # )()
})
# }, qsub_environment = list2env(lst(method_ti_methods, tasks, metric_names, method_params)), qsub_config = qsub::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```

@@

```{r fig.height=10, fig.width=10}
scores %>% left_join(tasks %>% select(id, trajectory_type), by=c("task_id"="id")) %>% 
  dplyr::select(-starts_with("time")) %>%
  gather(score_id, score, -method_name, -method_short_name, -method_id, -task_id, -error, -warning, -model, -trajectory_type) %>%
  filter(score_id %in% c("errored", "correlation", "robbie_network_score", "mean_R_nx")) %>% 
  ggplot() + geom_bar(aes(method_name, score, fill=score_id), stat="identity") + 
  facet_grid(trajectory_type~score_id) + coord_flip()
```

>>>>

data("toy_datasets")
datasets <- toy_datasets
```

```{r}
datasets$counts <- map(datasets$counts, function(counts) {
  cbind2(counts, matrix(sample(1:100, nrow(counts)*100, replace=TRUE), nrow=nrow(counts))) %>% {magrittr::set_colnames(., paste0("G", 1:ncol(.)))}
})
dataset <- dynutils::extract_row_to_list(datasets, 3)
pheatmap::pheatmap(dataset$counts)

source("~/thesis/projects/dynverse/dynmodular/dimred_wrappers.R")
# space <- dataset$counts %>% dimred_dp(2, neigen=2) %>% as.data.frame
space <- dataset$counts %>% dimred_mds(2) %>% as.data.frame
# space <- dataset$counts %>% dimred_lle(2) %>% as.data.frame
space <- space %>% bind_cols(dataset$prior_information$grouping_assignment %>% slice(match(rownames(dataset$counts), cell_id)))
space %>%  ggplot() + geom_point(aes(Comp1, Comp2, color=group_id))
```

@@

  # factory(function() {
    dyneval:::evaluate_ti_method(datasets, method, params, metrics = metric_names, timeout = 100)
  # }
  # )()
})
# }, qsub_environment = list2env(lst(method_ti_methods, datasets, metric_names, method_params)), qsub_config = qsub::override_qsub_config(memory = "10G", execute_before=c("module load python/x86_64/3.5.1"), wait=F))
```

@@

```{r fig.height=10, fig.width=10}
scores %>% left_join(datasets %>% select(id, trajectory_type), by=c("dataset_id"="id")) %>% 
  dplyr::select(-starts_with("time")) %>%
  gather(score_id, score, -method_name, -method_short_name, -method_id, -dataset_id, -error, -warning, -model, -trajectory_type) %>%
  filter(score_id %in% c("errored", "correlation", "robbie_network_score", "mean_R_nx")) %>% 
  ggplot() + geom_bar(aes(method_name, score, fill=score_id), stat="identity") + 
  facet_grid(trajectory_type~score_id) + coord_flip()
```

### 2018-07-05 scripts/manual_ti/guide.Rmd
dataset -> task

```{r setup, include=FALSE}
library(dynalysis)
library(tidyverse)

tasks_control <- read_rds(derived_file("tasks.rds", "1-datasets/control"))
space <- tasks_control %>% filter(id == "control_bifurcating") %>% pull(space) %>% first()
```

>>>>

```{r setup, include=FALSE}
library(dynbenchmark)
library(tidyverse)

datasets_control <- read_rds(derived_file("datasets.rds", "1-datasets/control"))
space <- datasets_control %>% filter(id == "control_bifurcating") %>% pull(space) %>% first()
```
